Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\noindent {\underline{\em Example 5.2.}} Segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has one left-covering rectangle in $R_2$, which is $\beta_1$. As the entire $h_2$ is covered by $\beta_1$, it is equivalent to its trimmed segment $h_2'$. Segment $h_3$ has two left-covering rectangles in $R_2$, which are $\beta_2$ and $\beta_3$.
\qed

@@

>>>>

\noindent {\underline{\em Example 5.2.}} In Figure~\ref{fig:guard}a, segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has one left-covering rectangle in $R_2$, which is $\beta_1$. As the entire $h_2$ is covered by $\beta_1$, it is equivalent to its trimmed segment $h_2'$; see Figure~\ref{fig:hv:type2:ex}b. Segment $h_3$ has two left-covering rectangles in $R_2$, which are $\beta_2$ and $\beta_3$. The right endpoint of its trimmed segment $h_3'$, as shown in Figure~\ref{fig:guard}b, is decided by the right edge of $\beta_3$. Therefore, $H' = \set{h_2', h_3'}$. It is clear from Figure~\ref{fig:guard}b that $\J(R_1, , H', V)$ has 3 tuples: $\bm{t}_1 = (\alpha, h_2', v_1), \bm{t}_2 = (\alpha, h_3', v_1)$, and $\bm{t}_3 = (\alpha, h_3', v_2)$.
\qed

@@

\noindent {\underline{\em Example 5.3.}} For $\bm{t}_1 = (\alpha, h_2', v_1) \in \J(R_1, , H', V)$.
Therefore, $H' = \set{h_2', h_3'}$. It is clear from Figure~\ref{fig:guard}b that $\J(R_1, , H', V)$ has 3 tuples: $\bm{t}_1 = (\alpha, h_2', v_1), \bm{t}_2 = (\alpha, h_3', v_1)$, and $\bm{t}_3 = (\alpha, h_3', v_2)$.
